---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

```

## Is it common to see a dog on a walk in NZ?
If yes, what breeds are we seeing more of? This report explores these questions based on data collected from a survey. 


These summary values show the minimum, maximum and mean amount of dogs seen on all recorded walks from the survey. On average 2.75 dogs are seen on a walk. You cannot see 0.75 of a dog so it is better to say: On average at least 2 dogs are seen on a walk.

```{r}
library(tidyverse)

# Read csv to get data directly from Google Sheet
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQgk9_5KnvFgJWo0KGoN_xy-OaKYOI86Efby3y83F4zmPjUYIgSY0Fn8s7WEuzYpls7Dlf879Bof_Ey/pub?output=csv")

# Rename variables and create new df
latest_data <- logged_data %>%
  rename(
    dog_amount = 2, 
    same_breed = 3,  
    which_breed = 4   
  )

# values for amount of dogs seen in total
min_dog_amount <- min(latest_data$dog_amount, na.rm = TRUE)
max_dog_amount <- max(latest_data$dog_amount, na.rm = TRUE)
mean_dog_amount <- mean(latest_data$dog_amount, na.rm = TRUE)

print(min_dog_amount)
print(max_dog_amount)
print(mean_dog_amount)
```

The first graph explores whether or not it is common to see the same dog breed on a walk. From the graph we can see that it is slightly more common to not see the same breed in one walk.

```{r}
library(tidyverse)

# Read csv to get data directly from Google Sheet
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQgk9_5KnvFgJWo0KGoN_xy-OaKYOI86Efby3y83F4zmPjUYIgSY0Fn8s7WEuzYpls7Dlf879Bof_Ey/pub?output=csv")

# Rename variables and create new df
latest_data <- logged_data %>%
  rename(
    dog_amount = 2, 
    same_breed = 3,  
    which_breed = 4   
  )

latest_data  %>% 
  ggplot() +
  geom_bar(aes(x = same_breed),
           fill = "pink")+
  labs(title = "Was the same breed of dog seen on one walk",
       caption = "Source: Survey",
       x = "Same breed",
       y = "Amount")

```

The second graph shows how many dogs were seen on a walk vs if there were duplicates of a single breed seen. As the amount of dogs seen on a walk increases, so does the likelihood that we will see at least 2 of the same breed. 

```{r}
latest_data %>% 
  ggplot() +
  geom_bar(aes(x = dog_amount, fill = same_breed)) +
  labs(title = "Dogs seen on a walk vs Same breed",
       caption = "Source: Survey",
       x = "Dog Breed",
       y = "Amount")

```






